\documentclass[a4paper, 10pt]{report}

\usepackage[right=1in, left=1in, top=1in, bottom=1in]{geometry}
\linespread{1.5}
\usepackage{amsmath, amsthm, amssymb} %math's packages
\usepackage[utf8]{inputenc} %document encoding

\usepackage{amsmath, amsthm, amssymb}
\usepackage{enumerate}
\usepackage{verbatim}
%\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{color}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{makecell}
\usepackage{colortbl}
\usepackage{booktabs}
%\usepackage{babel}
\usepackage{array,multirow,graphicx}
\usepackage{tikz}
\usepackage[most]{tcolorbox} %using color boxes
\usepackage{pgfplots} %plots
\usepackage{standalone} %including other files without preambule
\usepackage{setspace}

\usetikzlibrary{arrows.meta}
\hyphenation{distributions}
\usetikzlibrary{arrows, positioning, shapes.geometric}
\newtheoremstyle{break}% name
{}%         Space above, empty = `usual value'
{}%         Space below
{\itshape}% Body font
{}%         Indent amount (empty = no indent, \parindent = para indent)
{\bfseries}% Thm head font
{.}%        Punctuation after thm head
{\newline}% Space after thm head: \newline = linebreak
{}%         Thm head spec

\graphicspath{ {./Plots_transfer/} }
%\usepackage[svgnames]{xcolor}
%\usepackage[round]{natbib}


\newcommand{\cov}{\mathbb{C}\text{ov}}
\newcommand{\eig}{\text{EIG}}
\newcommand{\ape}{\text{APE}}
\newcommand{\kl}[2]{\text{KL}\left(\ #1\ ||\ #2\ \right)}
\newcommand{\entropy}[1]{H\left(\ #1\ \right)}
\newcommand{\expect}{\mathbb{E}}	
\newcommand{\R}{\mathbb{R}}
\newcommand{\prob}{\mathbb{P}}	
\newcommand{\tP}{\tilde{P}}	
\newcommand{\tPg}{\tilde{P}_{\gamma}}	
\newcommand{\tpi}{\tilde{\pi}}	
\newcommand{\tpig}{\tilde{\pi}_{\gamma}}
\newcommand{\tpigLi}{\tilde{P}_{\gamma,L,i}} 
\newcommand{\tpigLk}{\tilde{P}_{\gamma,L,k}} 
\newcommand{\tpigJi}{\tilde{P}_{\gamma,J,i}} 
\newcommand{\tpigJk}{\tilde{P}_{\gamma,J,k}} 
\newcommand{\RJi}{R_{\gamma,J,i}} 
\newcommand{\RJk}{R_{\gamma,J,k}}
\newcommand{\RLi}{R_{\gamma,L,i}} 
\newcommand{\RLk}{R_{\gamma,L,k}}
\newcommand{\Qgi}{Q_{\gamma,i}} 
\newcommand{\Qgk}{Q_{\gamma,k}}

\newcommand{\agi}{a_{\gamma,i}} 
\newcommand{\agk}{a_{\gamma,k}}  
\newcommand{\agj}{a_{\gamma,j}}  
\newcommand{\wgi}{w_{\gamma,i}} 
\newcommand{\wgk}{w_{\gamma,k}}
\newcommand{\wgj}{w_{\gamma,j}}
\newcommand{\giY}{\gamma \in \mathcal{Y}} 
\newcommand{\bb}[1]{\mathbb{#1}}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}%[section]
\newtheorem{assu}[thm]{Assumption}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
%
\theoremstyle{definition}
\newtheorem{ex}[thm]{Example}
\newtheorem{defi}[thm]{Definition}
\newtheorem{alg}{Algorithm}
%
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\renewcommand{\baselinestretch}{1.5}

\begin{document}
	
	\include{title_page}
	
	\tableofcontents
	
\newpage
	\chapter*{Acknowledgements}
	\addcontentsline{toc}{chapter}{Acknowledements}
	I have been fortunate, in the first year of my DPhil, to have worked with a number of brilliant people. First and foremost, I would like to acknowledge the support, advice and patience of my supervisor, Yee Whye Teh. Also within Oxford, both Benjamin Bloem-Reddy and Tom Rainforth have been incredibly generous with their time and expertise. Without them, I would have struggled to achieve much in my first year. I would also like to thank Emile Mathieu for his unwavering support and friendship. I am grateful to Noah Goodman for taking a gamble on an unknown DPhil student and supporting my application to Uber Technologies for an internship. Noah's enthusiasm and guidance made my internship a joy, and also set me on a new and exciting research path. I'd like to extend my thanks to Martin Jankowiak and Eli Bingham, as well as the whole pyro team, for their continued help and support.
	
	
	%The author would like to thank his supervisor, Professor , for his assistance and detailed feedback. 
	%\newpage
	
	\chapter*{Preface}
	\addcontentsline{toc}{chapter}{Preface}
	\label{chap:preface}
	\input{preface}
	
	\chapter{Introduction and literature review}
	\label{chap:intro}
	\input{intro}
	
	\chapter{Probabilistic modelling and inference}
	\label{chap:probabilistic_modelling}
	\input{probabilistic_modelling}
	
	\chapter{Probabilistic programming}
	\label{chap:ppl}
	\input{ppl}
	
	\chapter{Optimal experiment design}
	\label{chap:oed}
	\input{oed}
	
	\chapter{Future directions}
	\label{chap:future}
	\input{future}
	
	\input{appendix}
	\clearpage %fixing numeration
	\addcontentsline{toc}{chapter}{Bibliography}
	
	\bibliography{referencs}
	\bibliographystyle{apalike}
	
\end{document}